\documentclass{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{calc}
\usepackage{enumitem}
\usepackage{hyperref}

\usepackage{titlesec}
\titleformat{name=\section}[display]
{\Large \scshape}
{}
{-\parskip}{}

\author{Adrian Parvin D. Ouano}
\usepackage{multicol}

\begin{document}
\pagenumbering{gobble}

\SetLabelAlign{parright}{\parbox[t]{\labelwidth}{\raggedleft#1}}

\setlist[description]{style=multiline,leftmargin=5cm,font=\normalfont\scshape,%
    align=parright}

\begin {center}
  \Huge \scshape Adrian Parvin D. Ouano
\end {center}

\hrulefill
\section*{Info and Contact Details}

\begin{description} \item [Place \& Date of Birth] Cebu City, Cebu on February 19, 1999
\item [Address] Lower Hermag, Tabok, Mandaue City
\item [Phone] +639053069532
\item [Email Address] \href{mailto:adrianparvino@gmail.com}{mailto:adrianparvino@gmail.com}
\item [Github] \href{https://github.com/adrianparvino}{https://github.com/adrianparvino}
\end{description}

\hrulefill
\section*{Related Skills}

Listed according to confidence:

\begin{multicols}{2}
\begin {enumerate}
\item Haskell
\item C
\item Nix and Nixops
\item Lua
\item \LaTeX
\item Rust
\item x86 ASM
\item HTML+CSS
\item Prolog
\item Bash
\end {enumerate}
\end{multicols}

\hrulefill
\section*{Freelancing Experience}

\begin{description}
\item [Private Startup Company] Project packaging and deployment through
  Nix and NixOps. Focus on automation of deployment and reproducibility of binaries.

\item [Legends of DOTA Redux] Functioned as project manager. Created the git
  discipline and handled general code quality control.

  \href{https://github.com/darklordabc/Legends-of-Dota-Redux}{https://github.com/darklordabc/Legends-of-Dota-Redux}
\end{description}

\hrulefill
\section*{Hobby Projects}

\begin {description}
\item [Hlibc] A libc implementation targetting Linux and C99. I am responsible
  for algorithms and refactoring of code in order to reflect more
  the intent of the programmer. I am also responsible for some of the operations
  with the use of the Nix tool.

  \href{https://github.com/cmgraff/hlibc}{https://github.com/cmgraff/hlibc}

\item [ASCIIVN] An ASCII art Visual Novel Engine Written in C.
  This code focuses on highly-performant C that utilizes compiler optimizations
  while keeping standards compatibility.
  This code was produced for our Senior High School research paper.

  \href{https://github.com/adrianparvino/asciivn}{https://github.com/adrianparvino/asciivn}

  \href{https://github.com/adrianparvino/asciivn-paper}{https://github.com/adrianparvino/asciivn-paper}

\end{description}
\end{document}
